---
title: "dataviz_tryout"
author: "Ajla Mujcic"
date: "20-5-2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

Does this setup-code always have to be included?
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data visualisation try-out

# Load packages
```{r}
library(readr)
library(tidyverse)
```

# Download texas_cancer data

Source: <https://www.cancer-rates.info/tx/>

removed first 2 rows from original .csv file: 

1. Invasive Cancer Incidence Rates by County in Texas
2. All Sites, 2012 - 2016

removed last 3 rows from original .csv file:

1. Note: All rates are per 100,000. Rates are age-adjusted to the 2000 U.S. Standard Population.
2. Rates generated on May 20, 2019.
3. Cancer Incidence File, Jan 2019.
```{r}
texas <- read.csv("C:/Users/Eigenaar/Documents/R cursus EUR/dataset cancer Texas.csv", header = TRUE, sep = ",")
str(texas)
head(texas)
texas2 <- read_csv("C:/Users/Eigenaar/Documents/R cursus EUR/dataset cancer Texas.csv")
head(texas2)
```

# Top 10 counties with largest cancer rate
```{r}
texas %>% summarise(max(Crude.Rate))
texas2 %>% summarise(max(`Crude Rate`))
texas2 %>% arrange(desc(`Crude Rate`)) %>% filter(`Crude Rate` >= 714)
```
Question: why is the tibble frame rounded to 835, and the dataframe not at 835.2.
Qestion: when are `` backticks needed around variable names for a tibble
Question: when in the middle of data analysis is a tibble to be preferred over a dataframe? Why?

# Top 10 counties with lowest cancer rate
```{r}
texas %>% summarise(min(Crude.Rate))
texas2 %>% summarise(min(`Crude Rate`))
texas2 %>% arrange(`Crude Rate`) %>% filter(`Crude Rate` <= 293)
```

# Data visualisation: show the different cancer rates, both crude and age adjusted for the 10 counties with the lowest cancer rate
```{r}
plot(texas$County, texas$Crude.Rate)
texas_ar <- texas2 %>% arrange(`Crude Rate`) %>% filter(`Crude Rate` <= 293)
texas_ar %>% ggplot(aes(x = reorder(`County`, `Crude Rate`), y = `Crude Rate`)) + geom_col() + labs (x = "Counties",
                                                                              y = "Crude cancer rates",
                                                                              title = "Top 10 Texas counties with lowest cancer rates") +
  theme_minimal()

```
str(texas2)

